```{r}
install.packages("boot",dep=TRUE)
install.packages("ggplot2")
install.packages("pryr")
install.packages("devtools")
devtools::install_github("hadley/lineprof")
```

```{r}
install.packages("pryr")
```

```{r}
library(pryr)
```


```{r}
write.csv(df, 'myDF.csv')
```

```{r}
install.packages("tidyverse")

```


```{r}

library(tidyverse)
```

```{r}
options(max.print=10000000)
```

read in raw data, Null_Touches.csv

```{r}
library(boot)
nullTouches <- read.csv("/Users/matt/ProjectRStuff/Null_Touches.csv")
```

we also need to read in our analysis csv, or else we would have to recompute number of commits that introduce nullcheckers.

```{r}
commitData <- read.csv("/Users/matt/eclipse-workspace/Commits_Null.csv")
```

```{r}
head(commitData)
```

```{r}
head(nullTouches)
```

Make list of repo names.  We will do analysis for each repo.

```{r}
repos <- unique(nullTouches$Repo)
```

Filter "repos" if there are not > 25 yesChecker commits
```{r}

repos
```


```{r}
reposFiltered <- commitData[commitData$Commits_Checkers > 25, ]

#reposFiltered

repos <- reposFiltered$Project
repos
length(repos)

```

```{r}
head(reposFiltered)
```

```{r}

```

We want to start making vectors of data that is of interest.  Our goal for this script will be to produce a csv file.



```{r}
commitsNullChecker <- (reposFiltered$Commits_Checkers)
```

```{r}
commitsNullChecker

```

```{r}

LOC_NChecker_Commits <- (reposFiltered$LOC_Checkers)
```

```{r}
Authors_NChecker_Commits <- (reposFiltered$Authors.Yes.Checker)

```  
  
```{r}

Committers_NChecker_Commits <- (reposFiltered$Committer.Yes.Checker)
```
  
```{r}
df <-cbind(df, Authors_NChecker_Commits)

```
  
```{r}
df <- cbind(df, totalCommits)
```


```{r}
df <- cbind(df, Authors_NChecker_Commits)
```

```{r}

how_Many_Nullcheckers <- (reposFiltered$How.Many.Nullchekcers)
```

```{r}
how_Many_Nullcheckers
```

```{r}
write.csv(df, 'myDF.csv')
```

```{r}

df = data.frame(repos, how_Many_Nullcheckers, commitsNullChecker)
write.csv(df, 'myDF.csv')
nrow(df)
```

```{r}
numCommits <- function(data){
  return(nrow(data))
}
```

```{r}
numCommits

```
define some functions to return bootstrap statistics as desired


```{r}

function_filesTouched_multiCommit <- function(data, index, numCommits){
  sum = 0
    subset <- data[sample(nrow(data), numCommits, replace = TRUE),]
    subList <- (subset$NumFiles)
    for (i in 1:numCommits){
      sum = sum + subList[[i]]
    }
    rm(subset)
    rm(subList)
    rm(data)
    #print("getting boot data")
    #gc()
  return(sum)
}
```

replace logic from Files_Touched for LOC

```{r}
function_LOC_multiCommit <- function(data, index, numCommits){
  sum = 0
    subset <- data[sample(nrow(data), numCommits, replace = TRUE),]
    subList <- (subset$Lines.of.Code.Added.or.Removed)
    for (i in 1:numCommits){
      sum = sum + subList[[i]]
    }
    rm(subset)
    rm(subList)
    rm(data)
    #print("getting boot data")
    #gc()
  return(sum)
}

```

multiCommit Author Counter function

```{r}

function_Authors_multiCommit <- function(data, index, numCommits){
  sum = 0
    subset <- data[sample(nrow(data), numCommits, replace = TRUE),]
    
    subList <- unique(subset$Author.Name)
    #for (i in 1:numCommits){
    #  sum = sum + subList[[i]]
   # }
    sum = length(subList)
    rm(subset)
    rm(subList)
    rm(data)
    #print("getting boot data")
    #gc()
  return(sum)
}


```

committers multiCommit
```{r}
function_Committers_multiCommit <- function(data, index, numCommits){
  sum = 0
    subset <- data[sample(nrow(data), numCommits, replace = TRUE),]
    
    subList <- unique(subset$Comitter.Name)
    #for (i in 1:numCommits){
    #  sum = sum + subList[[i]]
   # }
    sum = length(subList)
    rm(subset)
    rm(subList)
    rm(data)
    #print("getting boot data")
    #gc()
  return(sum)
}


```


We need a function that will get number of files affected by commits that add null checkers.

```{r}
function_numFiles <- function(data){
  sum = 0
  subset <- data[data$NullCheckers. == "Yes",]
  #length(subset)
  subList <- (subset$NumFiles)
  for (i in 1: length(subList)){
    sum = sum + subList[[i]]
  }
  print("computing files")
  rm(subset)
  rm(subList)
  rm(data)
  gc()
  return(sum)
}

```


```{r}
function_LOC <- function(data){
  sum = 0
  subset <- data[data$NullCheckers. == "Yes",]
  #length(subset)
  subList <- (subset$Lines.of.Code.Added.or.Removed)
  for (i in 1: length(subList)){
    sum = sum + subList[[i]]
  }
  print("computing LOC")
  rm(subset)
  rm(subList)
  rm(data)
  gc()
  return(sum)
}


```

We have the unique repo names (repos) and how many commits for each one added null checkers (commitCheckerNums).  The next step is to take a subset of our data for one repo.

```{r}

totalCommits <- vector()
commitsIntroduceNull <- vector()
files_Touched_NChecker_Commits <- vector()
bsFileMedians <- vector()

filePVals <- vector()

```

```{r}
totalCommits
```
get authors for NCheckers from nulltouches
```{r}
Authors_NChecker_Commits <- vector()
for (i in 1:length(repos)){
  repoName <- repos[[i]]
  dataSubSet <- nullTouches[nullTouches$Repo == repoName & nullTouches$NullCheckers. == "Yes",]
  #Authors_NChecker_Commits <- append(Authors_NChecker_Commits, )
  subList <- unique(dataSubSet$Author.Name)
    #for (i in 1:numCommits){
    #  sum = sum + subList[[i]]
   # }
    sum = length(subList)
    Authors_NChecker_Commits <- append(Authors_NChecker_Commits, sum)
    rm(dataSubSet)
    rm(subList)
    gc()
  
}
length(Authors_NChecker_Commits)

```
get committers for NChecker commits from Nulltouches
```{r}
Committers_NChecker_Commits <- vector()
for (i in 1:length(repos)){
  repoName <- repos[[i]]
  print(repoName)
  dataSubSet <- nullTouches[nullTouches$Repo == repoName & nullTouches$NullCheckers. == "Yes",]
  #Authors_NChecker_Commits <- append(Authors_NChecker_Commits, )
  subList <- unique(dataSubSet$Comitter.Name)
    #for (i in 1:numCommits){
    #  sum = sum + subList[[i]]
   # }
    sum = length(subList)
    print(sum)
    Committers_NChecker_Commits <- append(Committers_NChecker_Commits, sum)
    rm(dataSubSet)
    rm(subList)
    gc()
  
}
length(Committers_NChecker_Commits)
```

```{r}

for (i in 1:length(repos)){
  repoName <- repos[[i]]
  dataSubSet <- nullTouches[nullTouches$Repo == repoName,]
  totalCommits <- append(totalCommits, numCommits(dataSubSet))
  rm(dataSubSet)
  #rm(totalCommits)
  gc()
}
```


Adding to dataframe, printing csv
```{r}

df <-cbind(df, totalCommits)


```

```{r}
df <- cbind(df, Committers_NChecker_Commits)
```

```{r}
write.csv(df, 'myDF.csv')
```

```{r}
  
for (i in 1:length(repos)){
  repoName <- repos[[i]]
  dataSubSet <- nullTouches[nullTouches$Repo == repoName,]
  filesActual <- function_numFiles(dataSubSet)
  files_Touched_NChecker_Commits <- append(files_Touched_NChecker_Commits, filesActual)
  rm(dataSubSet)
  rm(filesActual)
  gc()
}
```

```{r}
length(files_Touched_NChecker_Commits)


```


```{r}
df <-cbind(df, files_Touched_NChecker_Commits)
write.csv(df, 'myDF.csv')

```


```{r}
df <- cbind(df, meanBootstrappedFiles)

```

```{r}
df <- cbind(df, pValFilesActual)

```

```{r}

df <- cbind(df, LOC_NChecker_Commits)
```

```{r}
write.csv(df, 'myDF.csv')

```

```{r}
meanBootstrappedFiles <- vector()
pValFilesActual <- vector()


```

```{r}
for (i in 1:length(repos)){
  repoName = repos[[i]]
  checkerNums = commitsNullChecker[[i]]
  dataSubSet <- nullTouches[nullTouches$Repo == repoName,]
  filesActual <- function_numFiles(dataSubSet)
  print("calling boot")
  print(i)
  bootcorr <- boot(dataSubSet, function_filesTouched_multiCommit, R=100000, numCommits=checkerNums)
  s1 <- "Filesmodifiedper"
  s2 <- toString(checkerNums)
  s3 <- "commits"
  s4 <- paste(s1, s2, s3, sep="")
  #str_remove(s4, "/")
  #s5 <- "Median: "
  s5 <- ".jpeg"
  s6 <- paste(repoName, s4, s5, sep="")
  
  s6 <- str_replace_all(s6, "([a-zA-Z])/([a-zA-Z])", "\\1\\2")
  s7 <- "jPegs/"
  s8 <- 
  print(s6)
  jpeg(file=s6)
  
  list_histo <- hist(bootcorr$t, prob = TRUE, breaks = 50,
     main=repoName, xlab = s4)
  dev.off()
  argmax <- which.max(list_histo$counts)
  center <- list_histo$mids[[argmax]]
  
  print("Mean")
  mean <- mean(bootcorr$t)
  print(mean)
  meanBootstrappedFiles <- append(meanBootstrappedFiles, mean)
  print("filesActual")
  print(filesActual)
  
  P = ecdf(bootcorr$t)
  if (filesActual > center){
    pVal <- 1 - P(filesActual)
  } else {
    pVal <- P(filesActual)
  }
  pValFilesActual <- append(pValFilesActual, pVal)
  print("p-value")
  print(pVal)
  rm(bootcorr)
  rm(dataSubSet)
  rm(filesActual)
  rm(list_histo)
  rm(P)
  gc()
  
}

```

```{r}

df <-cbind(df, meanBootstrappedFiles)
df <- cbind(df, pValFilesActual)
write.csv(df, 'myDF.csv')

```

Replicate bootstrapping for LOC

```{r}

meanBootstrappedLOC <- vector()
pVal_LOC_Actual <- vector()
```

LOCs!!

```{r}
df <- cbind(df, meanBootstrappedLOC)
```

```{r}
df <- cbind(df, pVal_LOC_Actual)

```

```{r}

df <- cbind(df, meanBootstrappedAuthors)
#df <- cbind(df, pVal_Authors_Actual)
#meanBootstrappedAuthors <- vector()
#pVal_Authors_Actual <- vector()

```

```{r}
df <- cbind(df, pVal_Authors_Actual)

```

```{r}
df <- cbind(df, Committers_NChecker_Commits)
```

```{r}
df <- cbind(df, meanBootstrappedCommitters)

```

```{r}
df <- cbind(df, pVal_Committers_Actual)
```
```{r}
df <- cbind(df, p_values_unadjusted)
```

```{r}
df <- cbind(df, p_values_LOC_unadjusted)
```

```{r}

df <- cbind(df, p_values_Files_unadjusted)
```


```{r}
df <- cbind(df, Files_BH_adjusted_pvalues)

```

```{r}
df <- cbind(df, LOC_NChecker_Commits)
```

```{r}
df <- cbind(df, LOC_BH_adjusted_pvalues)
```

```{r}
df <- cbind(df, p_values_Authors_unadjusted)
```

```{r}
df <- cbind(df, Authors_BH_adjusted_pvalues)
```

```{r}
Authors_BH_adjusted_pvalues
```

```{r}
write.csv(df, 'myDF.csv')

```

```{r}
LOC_NChecker_Commits <- vector()

```

```{r}
for (i in 1:length(repos)){
  repoName = repos[[i]]
  #checkerNums = commitsNullChecker[[i]]
  dataSubSet <- nullTouches[nullTouches$Repo == repoName,]
  LOC_Actual <- function_LOC(dataSubSet)
  LOC_NChecker_Commits <- append(LOC_NChecker_Commits, LOC_Actual)
 # print("calling boot")
 # print(i)
 # bootcorr <- boot(dataSubSet, function_LOC_multiCommit, R=100000, numCommits=checkerNums)
 # s1 <- "LOC modified per "
 # s2 <- toString(checkerNums)
 # s3 <- " commits"
 # s4 <- paste(s1, s2, s3, sep="")
  #s5 <- "Median: "
 # list_histo <- hist(bootcorr$t, prob = TRUE, breaks = 50,
 #    main=repoName, xlab = s4)
 # argmax <- which.max(list_histo$counts)
 # center <- list_histo$mids[[argmax]]
  
 # print("Mean")
 # mean <- mean(bootcorr$t)
 # print(mean)
 # meanBootstrappedLOC <- append(meanBootstrappedLOC, mean)
 # print("LOCActual")
 # print(LOC_Actual)
  
 # P = ecdf(bootcorr$t)
 # if (LOC_Actual > center){
 #   pVal <- 1 - P(LOC_Actual)
 # } else {
  #  pVal <- P(LOC_Actual)
  #}
 # pVal_LOC_Actual <- append(pVal_LOC_Actual, pVal)
 # print("p-value")
 # print(pVal)
 # rm(bootcorr)
 # rm(dataSubSet)
 # rm(LOC_Actual)
 # rm(list_histo)
 # rm(P)
 # gc()
}
length(LOC_NChecker_Commits)
```


```{r}

meanBootstrappedAuthors <- vector()
pVal_Authors_Actual <- vector()

```

```{r}

meanBootstrappedCommitters <- vector()
pVal_Committers_Actual <- vector()

```

Authors

```{r}
p_values_Authors_unadjusted <- vector()
for (i in 1:length(repos)){
  repoName = repos[[i]]
  checkerNums = commitsNullChecker[[i]]
  dataSubSet <- nullTouches[nullTouches$Repo == repoName,]
  #dataSubSet <- nullTouches[nullTouches$Repo == repoName & nullTouches$NullCheckers. == "No",]
  Authors_Actual <- Authors_NChecker_Commits[[i]]
  print("calling boot")
  print(i)
  bootcorr <- boot(dataSubSet, function_Authors_multiCommit, R=100000, numCommits=checkerNums)
  #s1 <- "Unique authors per "
  #s2 <- toString(checkerNums)
  #s3 <- " commits"
  #s4 <- paste(s1, s2, s3, sep="")
  #s5 <- "Median: "
  #list_histo <- hist(bootcorr$t, prob = TRUE, breaks = 50,
   #  main=repoName, xlab = s4)
 # argmax <- which.max(list_histo$counts)
 # center <- list_histo$mids[[argmax]]
  
  #print("Mean")
  #mean <- mean(bootcorr$t)
 # print(mean)
 # meanBootstrappedAuthors <- append(meanBootstrappedAuthors, mean)
  print("AuthorsActual")
  print(Authors_Actual)
  
  P = ecdf(bootcorr$t)
 # if (Authors_Actual > center){
  #  pVal <- 1 - P(Authors_Actual)
 # } else {
    pVal <- P(Authors_Actual)
 # }
  p_values_Authors_unadjusted <- append(p_values_Authors_unadjusted, pVal)
  print("p-value")
  print(pVal)
  rm(bootcorr)
  rm(dataSubSet)
  rm(Authors_Actual)
  rm(list_histo)
  rm(P)
  gc()
}
length(p_values_Authors_unadjusted)


```


Committers

```{r}
p_values_Committers_unadjusted <- vector()
for (i in 1:length(repos)){
  repoName = repos[[i]]
  checkerNums = commitsNullChecker[[i]]
  dataSubSet <- nullTouches[nullTouches$Repo == repoName & nullTouches$NullCheckers. == "No",]
  Committers_Actual <- Committers_NChecker_Commits[[i]]
  print("calling boot")
  print(i)
  bootcorr <- boot(dataSubSet, function_Committers_multiCommit, R=100000, numCommits=checkerNums)
  #s1 <- "Unique committers per "
 # s2 <- toString(checkerNums)
 # s3 <- " commits"
 # s4 <- paste(s1, s2, s3, sep="")
  #s5 <- "Median: "
 # list_histo <- hist(bootcorr$t, prob = TRUE, breaks = 50,
 #    main=repoName, xlab = s4)
  #argmax <- which.max(list_histo$counts)
  #center <- list_histo$mids[[argmax]]
  
  #print("Mean")
  #mean <- mean(bootcorr$t)
 # print(mean)
  #meanBootstrappedCommitters <- append(meanBootstrappedCommitters, mean)
  print("CommittersActual")
  print(Committers_Actual)
  
  P = ecdf(bootcorr$t)
  #if (Committers_Actual > center){
  #  pVal <- 1 - P(Committers_Actual)
 # } else {
    pVal <- P(Committers_Actual)
 # }
  p_values_Committers_unadjusted <- append(p_values_Committers_unadjusted, pVal)
  print("p-value")
  print(pVal)
  rm(bootcorr)
  rm(dataSubSet)
  rm(Committers_Actual)
  #rm(list_histo)
  rm(P)
  gc()
}


```

testing
```{r}
function_WC_Files <- function(input){
  #sum = 0
  #yesCheckers <- data[data$NullCheckers. == "Yes",]
 # noCheckers <- data[data$NullCheckers. == "No",]
  
 # filesYesCheckers <- (yesCheckers$NumFiles)
  #filesNoCheckers <- (noCheckers$NumFiles)
  result <- wilcox.test(NumFiles ~ NullCheckers., data=input)
  
  #length(subset)
  #subList <- (subset$Lines.of.Code.Added.or.Removed)
  #for (i in 1: length(subList)){
  #  sum = sum + subList[[i]]
 # }
  #print("computing LOC")
  rm(input)
  #rm(subList)
  #rm(data)
  gc()
  #return(sum)
}
```

```{r}
p_values_Files_unadjusted <- vector()
```

```{r}

p_values_Files_unadjusted
```


```{r}
length(repos)
```

```{r}
  for (i in 1:length(repos)){
    repoName = repos[[i]]
    repoName
 # checkerNums = commitCheckerNums[[1]]
    dataSubSet <- nullTouches[nullTouches$Repo == repoName,]
  #numsActual <- function_numFiles(dataSubSet)
  #function_WC_Files(dataSubSet)
    dataSubSet$NullCheckers. <- factor(dataSubSet$NullCheckers., levels=c("Yes", "No"))
    #levels(dataSubSet$NullCheckers.)
  
    result <- wilcox.test(NumFiles ~ NullCheckers., data = dataSubSet, alternative = c("greater"), paired = FALSE)$p.value
    #print(result)
    p_values_Files_unadjusted <- append(p_values_Files_unadjusted, result)
    rm(dataSubSet)
    rm(result)
    gc()
  #set.seed(10)
  #bootcorr <- boot(dataSubSet, function_filesTouched_multiCommit, R=10000, numCommits=checkerNums)
  #dataSubSet
  #boot
  #bootcorr
  #bootcorr <- as.numeric(bootcorr)
  #hist(bootcorr)
  #plot(main = "title", bootcorr, index = 1)
  #s1 <- "Files modified per "
 # s2 <- toString(checkerNums)
 # s3 <- " commits"
 # s4 <- paste(s1, s2, s3, sep="")
 # s5 <- "Mean: "
 # print(s5)
  #mean(bootcorr$t)
  
 # t.test(bootcorr$t, mu=0)
  #list_histo <- hist(bootcorr$t, prob = TRUE, breaks = 50,
  #   main=repoName, xlab = s4)
  #list_histo
  #argmax <- which.max(list_histo$counts)
 # center <- list_histo$mids[[argmax]]
 # P = ecdf(bootcorr$t)
  
  #if (numsActual > center){
  #  pVal <- 1 - P(numsActual)
  #} else {
 #   pVal <- P(numsActual)
 # }
 # pVal
  
  #plot(P)
  
  #bootcorr$t
  #summary(bootcorr)
  #t
  }
length(p_values_Files_unadjusted)
```
```{r}
p_values_LOC_unadjusted <- vector()

```


loc
```{r}

for (i in 1:length(repos)){
    repoName = repos[[i]]
    repoName
 # checkerNums = commitCheckerNums[[1]]
    dataSubSet <- nullTouches[nullTouches$Repo == repoName,]
  #numsActual <- function_numFiles(dataSubSet)
  #function_WC_Files(dataSubSet)
    dataSubSet$NullCheckers. <- factor(dataSubSet$NullCheckers., levels=c("Yes", "No"))
    #levels(dataSubSet$NullCheckers.)
  
    result <- wilcox.test(Lines.of.Code.Added.or.Removed ~ NullCheckers., data = dataSubSet, alternative = c("greater"), paired = FALSE)$p.value
    #print(result)
    p_values_LOC_unadjusted <- append(p_values_LOC_unadjusted, result)
    rm(dataSubSet)
    rm(result)
    gc()
}
length(p_values_LOC_unadjusted)

```


```{r}
Files_BH_adjusted_pvalues <- vector()
```

```{r}

Files_BH_adjusted_pvalues <-p.adjust(p_values_Files_unadjusted, method = "BH")

```

```{r}
Authors_BH_adjusted_pvalues <- vector()
Authors_BH_adjusted_pvalues <- p.adjust(p_values_Authors_unadjusted, method = "BH")
length(Authors_BH_adjusted_pvalues)
```

```{r}
LOC_BH_adjusted_pvalues <- vector()
LOC_BH_adjusted_pvalues <- p.adjust(p_values_LOC_unadjusted, method = "BH")
length(LOC_BH_adjusted_pvalues)

```

```{r}

Files_BH_adjusted_pvalues
```
```{r}
install.packages("sgof")
```
```{r}
version
```


```{r}
ls()

```

```{r}
ls()

```

```{r}


```